Stepwise Multiple Regressions

### 2021-02-10 Stepwise Multiple Regressions.Rmd
Example Plots for the interactions between dose and size

# Model: Crustacean Fitness, Organism Level Endpoints Only

@@

#Select the columns that we want to feed into the model for simplicity
m1_crust_simple <- aoc_setup %>%
  filter(!effect_f == "NA") %>%
  filter(!acute.chronic_f == "Unavailable") %>%
  filter(bio.org == "organism") %>%
  filter(!environment == "Terrestrial") %>%
  filter(lvl1_f == "Fitness") %>%
  filter(!size_f == "Not Reported") %>%
  mutate(logdose.mg.L.master = log10(dose.mg.L.master))

#Fit the full model
m1_crust_model_dose <- glm(effect_10 ~ logdose.mg.L.master + size.length.um.used.for.conversions, data = m1_crust_simple, na.action = "na.exclude", family = "binomial")

@@

#Plots
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)

range(m1_crust_simple$logdose.mg.L.master, na.rm = TRUE)
#[1] -11.638272   8.171552
# generate sequence of values between range in increments of 100 to give smooth appearance to model
xdose <- seq(-11.638272 ,8.171552, 0.1)
ydose <- predict(m1_crust_model_dose, 
                 list(logdose.mg.L.master = xdose), 
                 type = "response")
#ggplot with logistic data
 plot(m1_crust_simple$logdose.mg.L.master, m1_crust_simple$effect_10, pch = 16, xlab = "log dose (mg/L)", ylab = "effect")
# lines(xdose, ydose)

ggplot(m1_crust_simple, aes(x = logdose.mg.L.master, y = effect_10))+
  geom_point() +
  stat_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE)

@@

>>>>

# Model: Crustacean Fitness, Organism Level Endpoints Only
## Dose (mass)

@@

#Select the columns that we want to feed into the model for simplicity
m1_crust <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.mg.L.master = log10(dose.mg.L.master)) %>%
  mutate(logdose.particles.mL.master = log10(dose.particles.mL.master)) %>%
  mutate(logdose.um3.mL.master = log10(dose.um3.mL.master)) %>%
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.mg.L.master, logdose.particles.mL.master, logdose.um3.mL.master, size.length.um.used.for.conversions)) %>% 
  drop_na()

#Fit the full model
m1_crust_model_dose <- glm(effect_10 ~ logdose.mg.L.master*size.length.um.used.for.conversions, data = m1_crust, na.action = "na.exclude", family = "binomial")

@@

```{r}
#Plots
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)
```

## Dose (count)

@@

#Select the columns that we want to feed into the model for simplicity
m1_crust <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.mg.L.master = log10(dose.mg.L.master)) %>%
  mutate(logdose.particles.mL.master = log10(dose.particles.mL.master)) %>%
  mutate(logdose.um3.mL.master = log10(dose.um3.mL.master)) %>%
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.mg.L.master, logdose.particles.mL.master, logdose.um3.mL.master, size.length.um.used.for.conversions)) %>% 
  drop_na()

#Fit the full model
m1_crust_model_dose <- glm(effect_10 ~ logdose.particles.mL.master*size.length.um.used.for.conversions, data = m1_crust, na.action = "na.exclude", family = "binomial")

```{r}
#Plots
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)
```

## Dose (volume)

#Select the columns that we want to feed into the model for simplicity
m1_crust <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.mg.L.master = log10(dose.mg.L.master)) %>%
  mutate(logdose.particles.mL.master = log10(dose.particles.mL.master)) %>%
  mutate(logdose.um3.mL.master = log10(dose.um3.mL.master)) %>%
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.mg.L.master, logdose.particles.mL.master, logdose.um3.mL.master, size.length.um.used.for.conversions)) %>% 
  drop_na()

#Fit the full model
m1_crust_model_dose <- glm(effect_10 ~ logdose.um3.mL.master*size.length.um.used.for.conversions, data = m1_crust, na.action = "na.exclude", family = "binomial")

```{r}
#Plots
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)
```
